Data Deduplication and Zipf-like Distribution in VM Cloud Storage

### 2012-01-30 vm_snapshot_sim/abstract.tex
First draft

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}
\begin{document}
\title{foo}
\author{bar}
\date{}
\maketitle

\begin{abstract}
Virtualization has became the engine behind many cloud computing platforms.
In a virtualized computing environment, virtual machines
operate on virtual disks, so backing up user data is done by constantly 
taking snapshots of those virtual disks. Because such VM snapshots are huge in
terms of both quantity and individual sizes, snapshot storage would cost tremendous amount 
of space without deduplication.
Current snapshot deduplication is mainly done through copy-on-write 
on fixed-size disk blocks. Such solutions are fast but unable to handle the
 cross VM and inner-block data duplications. In addition, storing VM images and their snapshots
in the same storage engine reduce the underline design flexibility since these two kinds of data
have distinct access requirements.

In this paper, we first perform a large scale study in production VM clusters 
to show that cross VM data duplication is severe due to they have large amount of
common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
to address the above problem efficiently.
We eliminate the majority of cross VM data duplication by pre-select
a small set of frequently seen chunks to dedup against, and we also remove
many inner-block duplication using smaller chunking granuarity and locality.
Experiment shows our design can achieve high deduplication ratio and throughput
without incuring significant overhead to the runtime VM environment.
\end{abstract}

\input{intro}
%\input{background}
\input{approach}
%\input{results}
\input{related}
%\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{dedup}
\end{document}

>>>>

\begin{abstract}
Virtualization has became the engine behind many cloud computing platforms.
In a virtualized computing environment, virtual machines
operate on virtual disks, so backing up user data is done by constantly 
taking snapshots of those virtual disks. Because such VM snapshots are huge in
terms of both quantity and individual sizes, snapshot storage would cost tremendous amount 
of space without deduplication.
Current snapshot deduplication is mainly done through copy-on-write 
on fixed-size disk blocks. Such solutions cannot handle the
 cross VM data duplication because VMs do not share any data. 
In addition, storing VM images and their snapshots
in the same storage engine reduce the underline design flexibility because 
these two kinds of data have distinct access requirements.

In this paper, we first perform a large scale study in production VM clusters 
to show that cross VM data duplication is severe due to they have large amount of
common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
to address the above problem efficiently.
We eliminate the majority of cross VM data duplication by pre-select
a small set of frequently seen data blocks to be shared globally, and we also remove
many cross snapshot duplication by using smaller chunking granuarity and locality.
Experiment shows our design can achieve high deduplication ratio with very limited 
amount of resources in large scale VM cloud environment.
\end{abstract}

### 2012-01-30 vm_snapshot_sim/approach.tex
First draft

\section{Approach}
\subsection{Similarity Detection}
Data locality is important to 
Bringing deduplication to a distributed environment may
break data locality because 
introduces several 
new problems. Former studies of centralized deduplication systems showed
 that spatial locality of 
data streams must be preserved. This is because the entire
 chunk hashes are too big to be loaded into memory, 
thus certain caching mechanism must be applied, and this require 
proximal chunk IDs to be stored at nearby places. 
Furthermore, if chunks are not stored on the disk
base on spatial locality, file read requests will result in entirely
 random disk access, since each data chunk is so small, that would 
become a disaster for any host file system.

\subsubsection{Granuarity}
Extreme binning uses files as the basic unit for
similarity detection, this simplifies the metadata management of
distributed storage because it only need to manage the mapping
 from files to their bins. However, this solution doesn't
consider the uncertainty of file sizes: it is possible that many similar big files
can be assigned to one container, thus some storage nodes may be overlaoded when
others are spare. For example, Amazon's S3 stores huge amount of
virtual machine images which are very similar, so those files will be assigned
to only a few nodes by the extreme binning.
Even those files can be evenly distributed to hundreds of nodes, the overall 
deduplication ratio won't be good since too much dulicates are tolerated.

We suggest that data segment at the size of several megabytes is the best unit for
similarity based deduplication. Sparse Indexing has already 
proved that content based chunking method can be also applied to break the list of
chunks into large segments, such that each segment contains a few hundred of small chunks.
Using such medium size segments as the basic unit for similarity detection could eliminate
disadvantages mentioned above, and doing so won't add  much computation cost
to the deduplication process.

\subsubsection{Signature Algorithm}
In general, we expect to generate a signature for each segments, such that if two segments
has a lot of chunks in common, there is a high probablity that their signatures are the same.
Since we represent segment as a list of chunks, the information available for generating 
signatures are the chunk hash values, chunk sizes, and offsets.

Extreme binning suggests the min-hash signature algorithm. By Broder's theorem, 
the probability that the smallest elements of two sets are identical, is equal to their Jaccard similarity coefficient.
Therefore they use the smallest chunk hash value as the signature to represent the whole file.

We propose a Size-based Similarity Detection (SSD) method, 
which is more storage specific because it uses the chunk size information. Intuitively if one segment is
only slightly modified, then most of the chunks should remain the same, thus their sizes should mostly remain the same.
Even modifications could change the chunk hash value, due to the modification resistant property of 
content based chunking algorithm, most of the time that chunk size is unchanged. Therefore if we want to 
generate a $n$ bit signature for a segment, we simply split the range of size evenly at logarithmic scale by $n$ , and count how many chunks
fall into each range. Then if that number is above average, we set the bit for that range as 1, otherwise 0, as shown
in figure.

By using the signature of segment to represent all of its chunks, Sloud clusters
segments that are highly similar into one container. Each container is the collection of 
segments that have the same signature. When a new segment arrives, it will be assigned by its signature to
the corresponding container which has chunks that are highly similar to it. Thus,  highly accurate deduplcation is achieved.
However, since every segment is only assigned to one container, if any of the its chunks do not 
exist in that container but exist elsewhere, they will be treated as new chunks, in other words, 
duplicates are allowed. Sloud trade such storage space efficiency for faster deduplication and  
fewer resources consumption such as RAM usage and disk access. In addition, we believe this is the best way to 
build distributed deduplication solution without losing data locality.

\subsection{Architecture}
We designed a distributed storage system, Sloud, to demonstrate the possibility of
providing scalibility to large scale deduplication systems. Sloud cluster similar segment into containers and store
those containers to the disk. The overall architecture is shown in .
Sloud uses a DHT service for node discovery and storage space partitioning, all nodes in Sloud are completely equal, 
there's no node that has special responsibilities.

At every storage node , we keep in memory a bloom filter and a segment index for every container, 
the rest of part of the container, including the chunk data and chunk index, are stored onto disk. When a new segment comes in, the segment index is used
for the first pass of deduplication, such that duplicate segments can be detected without looking below. The second pass is done by bloom filter,
most of new chunks are immediately identified. Otherwise, Sloud look into the chunk index for the final pass of deduplication, as shown in Figure.

Assuming all node are reliable, no failure ever happens, and there is no replication involved, 
the deduplication process can be described as following:
\begin{enumerate}
\item Firstly,  sender scan the files that to need be deduplicated, generate all information about chunks and segments.
\item For each segment, sender queries the DHT service to find out the node that is responsible to segment's container, then it will send a segment writting message with segment's signature and hash.
\item The receiver then lookup corresponding container's segment index to see if its a duplicate. If it is, there is no need for further deduplication, it will update the segment's reference count and acknowledge the sender deduplication is complete.
\item If the segment hash does not exist in segment index, receiver asks sender for the segment recipe, which is all the chunks' information except the actual data.
\item On receiving the segment recipe, receiver starts deduplicate them against existing chunks in that container. Firstly it goes to the bloom filter, most of the new chunks are identified in this step. For those chunks that are identified as 'exist' by the bloom filter, the receiver looks into chunk index to see if they are really there or not. At any step, if a chunk is identified as new, a request of chunk data is immdeiately sent out.
\item Incoming chunk data are written to a temporary disk place until all new chunks belonging to that segment are received. Upon this time, receiver merges new data into that container's disk file.
\item Finally the receiver update the segment index and chunk index, and acknowledge the sender this segment is sucessfully received and deduplicated.
\end{enumerate}

\subsection{Replication and Concistency}
Sloud uses consistent hashing ring\cite{consistent_hash97} to maintain a dynamic hash table for node discovery. 
Each node is given an unique ID and the Sha-1 checksum of their IDs are mapped onto this ring. 
Containers are also mapped onto the consistent hash ring by the Sha-1 checksum of their represented signatures.
The benefit of using consistent hash is that adding or removing nodes from the system won't introduce too much
workload of reorganization. For each container on the ring, Sloud treat the first three consequential nodes as 
the primary replicas of that container, and the next two nodes as the secondary replicas. Primary replicas hold
the real copy of container's data, the secondary replicas are only used to cache write requests when some of the 
primary replicas are temporarily unavailable.

Sloud provides a variation of eventual consistency\cite{eventually09} in its data replication. Read
requests will succeed if at least one of the three primary replicas is available, write requests requires
the majority of five primary and secondary replica nodes to be available, which means one of the primary replicas
must be available for the write request.
During a segment write, sender finds out the first available node in three of primary replicas, say node A, 
and let this node handle the rest of deduplication and replication process. Node A will first deduplicate
the new segment as described in previous sections, then it tries to acknowledge other two primary replicas
about this update. If succeed, then this segment is successfully written. Otherwise it will
try to write this update to secondary replicas in order to make sure the new data is written to three places.
Upon a successful writting to both primary and secondary replicas with three copies, node A can tell the sender
the new segment is added to storage. But if the sender can not find a available primary replica node, or node A
can not write to the other two replicas, then the write request will fail.

When secondary replicas receive a segment write request, it will only cache the data because they do not have
that container. They will try to send cached requests to primary replicas when possible.
However, if two secdonary replicas want to acknowledge a recently recovered primary replica about the lastest updates,
the recovered node will receive duplicate requests.
Furthermore, it is possible that multiple senders want to write identical segment simultaneously, so it is necessary to use an ID
to distinguish every unique segment writting process.
In Sloud this segment process ID (SPID) is composed of sender's node ID and an incremental logical clock. The SPID is used through out that segment's
deduplication process and carried by all related messages.
In order to avoid processing the same request twice, for every segment Sloud keeps
its recent SPIDs in the segment index for a short period, therefore if the SPID of incoming segment writting request is found in segment index, 
receiver could know it has already received and deduplicated this segment.

Periodically, Sloud synchronize each container among its replicas. Synchronization requires
all primary and secondary replicas to be available. During this process, 
primary replicas compare each others' recent SPIDs along with secondary replica's cache to determine which write request it has missed. 
Upon a successful synchronization, all cached segment updates are ensured
to be delivered to three primary replicas, thus the secondary replicas' cachecan be cleaned up. In addition,
recent SPIDs in segment index is also stale, they will be cleaned up so that Sloud do not need to keep too many recent SPIDs
in segment index. If any node is not available during the synchronization, this process will fail. However, the primary replicas
still try to synchronize as much data as possible, except that the cache and SPIDs will not be cleaned up.

>>>>

\section{Our Approach}
\subsection{Aliyun's VM Cloud}
Aliyun provides the largest public VM cloud in China which is based on the 
open-source Xen technology. A typical VM cluster in our cloud environment
consists of from hundreds to thousands physical machines, each of which can
host tens of virtual machines. A few varieties of mainstream OS are supported,
including several editions of Windows Server, major Linux distributions, and FreeBSD.
During the VM creation, user choose his flavor of OS distribution, our system will
copy the corresponding pre-configured base VM image to his VM as the OS disk, 
and an empty data disk is created and mounted onto his VM as well.

\begin{figure}
  \centering
  \epsfig{file=images/tapdisk.eps, height=2in, width=2.66in}
  \caption{I/O channel between VM and image files}
  \label{fig:tapdisk}
\end{figure}

All these virtual disks are represented as virtual machine image files in our
underline runtime VM storage system. The runtime I/O between virtual machine and its virtual
disks is tunneled by the TapDisk driver. To avoid network latency and congestion, 
our distributed file system carefully selects the location of primary replica of VM's 
image files such that they are located on the same physical machine of VM instance.

Inside the TapDisk driver, we maintain an array of \emph{dirty bits} to record the dirty area
of runtime VM image file since the last snapshot, each bit represent a 2MB fix-sized
data segment. During a snapshot operation, we only need to look at the dirty region
rather than scan over the whold image file, which would be extremely slow.

The snapshot storage system also resides in our distributed file system, just like the 
runtime VM storage. But the difference is that snapshot storage do not need to be
co-located with VM instances, in fact they can even live in a different cluster to improve the 
data safty. When cluster A is offline, we can quickly restore its VMs from cluster B
to reduce the impact to our users.

The detail design and implementation of our distributed file system and various 
storage subsystems would be too complicated to be intorduced here, and also beyond
the scope of this paper. In the remaining section we will brief the model and interface of 
our snapshot storage.

\subsection{Snapshot Representation}
Each snapshot is a two-level index data structure in the form of HDAG. 
At the bottom level is variable-sized data blocks, like many other deduplication storage systems, 
we use 4KB as the average block size.
In the middle is the segment layer, a segment contains hundreds of blocks, it records the list
of block hash, data reference and some other meta information in a data structure we called
segment recipe. Then the segment recipe itself, can be serialized into a data block, so the hash
of segment recipes and their meta data formed the snapshot recipe. We take this two-level
structure because in practice we observed that at each snapshot only a small fraction
of dirty bits array are marked as set, so snapshot recipes can share the unmodified
segment recipes to reduce the space cost of snapshot meta data.

Instead of using variables-sized segment like many others did, we take the simpler approach
to let every segment being aligned to the boundary of dirty bits array. This is because
\emph{vhd} file format will keep the allocated inner blocks at the same positions until deletion,
which means the locality of snapshot data is almost natively aligned. Enforcing a boundary at every 2MB will
only break 0.2\% of total data blocks which is tiny.

\subsection{Snapshot Storage}
The snapshot storage system sits on top of our distributed file system, 
it can be abstracted as a block store which operates a few \emph{append-only} files
in the underline file storage. Each virtual disk has its own data store, all data 
blocks after deduplication will be stored into that system.

\begin{figure}
  \centering
  \epsfig{file=images/storage_overview.eps, height=2in, width=2.66in}
  \caption{Storage architecture}
  \label{fig:arch}
\end{figure}

We let each virtual disk has its own block store rather than sharing for several reasons:
first, all data written to block store are already being processed by deduplication
process, thus no sharing is necessary unless we want to perform additional deduplication
inside the block store. Second, such seperation will facilitate VM data stastics, 
deletion and migration. Finally, this reduces the complexity of concurrent snapshot operations.

The main interface of our snapshot storage is \emph{get}, \emph{put} and \emph{delete}.
Get interface accepts a piece of data, write it to the underline data file, and return
a reference to the caller. This reference then can be used in the put interface to
retrive or delete the data, thus the caller of put interface must preserve the
data reference for future use. Since all the underline data structures is append only,
upon a delete request, the corresponding data will only be marked rather than being deleted.
A compaction will take place when deleted data has accumulated to certain threshold, thus 
reclaiming the disk space .

In addition to above data access interfaces, the snapshot storage also supports
\emph{scan} and \emph{quota} methods. Scan allows us to traverse all the data blocks
that store in the data store, and quota is used to acknowledge user how much space he
has actually used.

\subsection{CDS Operations}
The CDS is divided into CDS meta and CDS data. THe structure of CDS meta is not different from the
segment recipe we discussed above, except that it is partitioned into many small slices so that each node
is easy to load its own slice. At the runtime, our CDS meta resides in a global shared memory cache for 
deduplication lookups. The data of CDS is stored in a special block store, which doesn't belong to any VM disk.

CDS meta assignment is done statically, each slice of CDS meta has one primary and two backup nodes.
During the system bootup, snapshot storage controller will read the assignment, 
load its primary portion of CDS meta from distributed file system. Loading the backup portion
of CDS is due upon a query arrives for it. Everyday the CDS assignment and CDS data will be checked
 for updates and reloaded if necessary.

Behind the scene there is a offline map-reduce job, which will periodically scan the block stores
in the entire cluster and perform a ``word counting''. High frequency blocks are then added to the CDS if its count 
 is greater than threshold, which is pre-defined by the system memory restrictions.

\subsection{Dedup Process}
Our deduplication process can be summarized as four steps:
\begin{list}{Dedup}{}
\item {Dirty bits: Copy the unchanged portion of snapshot recipe from parent snapshot, base on dirty bits.}
\item {Locality: Divide dirty segments into blocks, compare to the corresponding segment recipe at the same position of parent snapshot, if duplicate, copy the data reference into segment recipe.}
\item {CDS: Check if this data exist in the CDS, if yes, copy the returned data reference. Otherwise, write data block to block store, save the returned reference into segment recipe.}
\item {Save meta: write down the segment recipes and snapshot recipe when finish.}
\end{list}

### 2012-01-30 vm_snapshot_sim/intro.tex
First draft

1.how virtual machines work on storage
2.cow and why they are not good
3.introduce dedup

Virtualization is the engine behind many today's cloud computing platforms.
Amazon and many others have provided clusters that host 
hundreds of thousand virtual machines(VM) which are dynamically created
by users. In such a 
each instance of a guest operating system stores a
file called a virtual disk (e.g. .vhd, .vmdk) on the host system

Because those virtual machines are stored in  maVirtualization provide

Backing user data on these virtual disks is quite different from traditional file system backup.

File storage is a critical component in cloud infrastructure, because users and applications expect a  
persistent place to store and share their data. 
But there can be a significant amount of data redundancy in the storage system
 because large number of users employ such systems for backups, 
and file data between different users may overlap especially when user base is huge. 
For example, in a VM-based cloud, users usualy backup their virtual machine images along with application data 
to a cloud file storage periodically. 
Therefore, improving the space efficiency is an 
important factor in designing a file storage service for cloud.

@@

In cloud storage, we are solving data deduplication problem in a different context of 
data stream deduplication (the D2D case). 
We now consider the case for file synchronization service designed to service fine-grained low-locality backup workloads. 
Such a workload consists of newly modified files, instead of large data streams, that arrive in random order from many clients. 
There is generally no locality between files that arrive in a given window of time. 
In the absence of locality, deduplication approach designed for D2D backups perform poorly.

In addition, file storage with deduplication allow a data chunk to be shared by many files,
this has not been a problem in D2D backup systems because they may use costly hardware components
and RAID to reduce the risk of data loss. Unlike D2D backup systems, cloud storage prefers 
low-cost hardware at large scale to achieve both performance and reliability. Without software
replication, data is fragile in the constant presense of disk or system failure.

Our solution, Sloud, is designed for data deduplication in cloud storage systems. 
Sloud exploits file similarity and only in-file data locality.
Like Sparse Indexing, it splits large files into small chunks and coarse-grain segments.
Sloud uses segment as the basic unit for storage allocation, thus avoiding the possibility that a set of 
similar large files may overload part of the system. 
Then a stastic based signature algorithm is used to cluster similar segments into containers
which are located at fixed places by stateless routing. When new segment comes in, 
Sloud finds the container which is most likely to have similar data, then it store new segment
to that container for chunk deduplication. By doing this Sloud trade deduplication space efficiency
for performance and simplicity. In addition, Sloud provides software replication and eventual consistency
to enhance file availability and integrity.
Experiments shows our solution achieves a balance of space efficiency, data reliability and load balancing.

>>>>

%1.how virtual machines work on storage
%2.cow and why they are not good
%3.introduce dedup

Virtualization is the engine behind many popular cloud computing platforms.
Amazon, Aliyun and many others have provided public VM clouds that host 
hundreds of thousand virtual machines(VM) which are dynamically created
by users. In such a virtualized environment,
each instance of guest operating system operates
on virutal disks, which are represented as
files called virtual disk image (e.g. .vhd, .vmdk) in the host operating system.
Because those virtual disk images are stored as files in the external storage,
backing up VM data in virtual disks is mainly done by taking snapshots
of virtual disk images,
which is quite different from traditional file system backup.

The most widely used snapshot method is copy-on-write (CoW). Upon VM image storage system receives a save snapshot request,
it freezes the state of that image file, then all consequent write request will result in the write region being copied
to a incremental snapshot data file. CoW method can finish a snapshot operation instantly, but it has several disadvantages:
first, CoW may affect the general I/O performance due to defered data coping. 
Second, CoW does not seperate backup data and runtime image data,
which have distinct access requirements: runtime image data is directly used by the running VM, 
thus need high throughput, and is very sensitive to latency,
such data must be served with hig cost hardware, but backup data generally only need fair aggregate throughput, 
is not sensitive to latency, thus can be stored in secondary storage devices.
Finally and most important, VM snapshots contain tremendous amount of data duplication, which is nearly impossible to tackle 
if these two kinds of data are tightly coupled together.

@@

In cloud storage, we are solving data deduplication problem in a different context of 
data stream deduplication (the D2D case). Because our snapshot storage servive is co-located with runtim VMs,
we have very limited amount of system resource to perform deduplication. For example,
on our typical 8-core, 48GB memory, 12TB disk server, there lives over 20 VMs who are hungrily eating
system resources: some are running map-reduce jobs, some are busy web servers, some are backend databases.
Any behavior that affects user VMs performance or stability is unacceptable.

### 2012-01-30 vm_snapshot_sim/main.tex
First draft

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}
\begin{document}
\title{foo}
\author{bar}
\date{}
\maketitle

\begin{abstract}
Virtualization has became the engine behind many cloud computing platforms.
In a virtualized computing environment, virtual machines
operate on virtual disks, so backing up user data is done by constantly 
taking snapshots of those virtual disks. Because such VM snapshots are huge in
terms of both quantity and individual sizes, snapshot storage would cost tremendous amount 
of space without deduplication.
Current snapshot deduplication is mainly done through copy-on-write 
on fixed-size disk blocks. Such solutions are fast but unable to handle the
 cross VM and inner-block data duplications. In addition, storing VM images and their snapshots
in the same storage engine reduce the underline design flexibility since these two kinds of data
have distinct access requirements.

In this paper, we first perform a large scale study in production VM clusters 
to show that cross VM data duplication is severe due to they have large amount of
common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
to address the above problem efficiently.
We eliminate the majority of cross VM data duplication by pre-select
a small set of frequently seen chunks to dedup against, and we also remove
many inner-block duplication using smaller chunking granuarity and locality.
Experiment shows our design can achieve high deduplication ratio and throughput
without incuring significant overhead to the runtime VM environment.
\end{abstract}

\input{intro}
%\input{background}
\input{approach}
%\input{results}
\input{related}
%\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{dedup}
\end{document}

>>>>

\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
%\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}
\begin{document}
\title{Data Deduplication and Zipf-like Distribution in VM Cloud Storage}
\author{Wei Zhang, Hong Tang, Hao Jiang, Rachael Zeng, Xiaogang Li, Tao Yang}
\date{}
\maketitle

\input{abstract}
\input{intro} %introduce the problem, related solutions and our requirements
\input{cds} %data study, zipf, model of cds size and dedup efficiency
\input{approach} %our dedup process
\input{results}
%\input{related}
%\input{future}
\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{dedup}
\end{document}
